An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
a
fix
additional fixes

Using the skeletonized word image, we now create a vertical projection histogram.
This vertical projection histogram takes the sum of every collumn in the image, counting black pixels as a $1$ value, and white pixels as a $0$ value.

We now regard the collumns with a total pixel count of zero or one pixel as potential segmentation points.
We interpret these collumn to be the whitespace in between characters or the line connecting two characters to each other.
This will inevitably cause oversegmentation in our word image.
The next step will be to filter the potential segmentation points, and remove the incorrect ones through postprocessing.

@@

\subsubsection{Rule based techniques}
The main oversegmentation correction is handled by our neural network.
However some simple preprocessing is added to remove obvious unwanted segmentation points.

>>>>

Using the skeletonized word image, we create a vertical projection histogram.
This vertical projection histogram counts the black pixels of every column in the image.
We regard the columns with a total pixel count of zero or one as potential segmentation points.
We interpret these columns as whitespace in between characters or as a line connecting two characters to each other.
This will inevitably cause oversegmentation in our word image.
The next step filters incorrect segmentation points caused by oversegmentation.

@@

\subsubsection{Rule based techniques}
Most of the oversegmentation correction is done by our neural network.
However some simple preprocessing is added to remove obvious unwanted segmentation points.
